\thetitle

### 2021-04-30 writing/challenges.tex
Use "semantic variants" instead of "soundness mechanisms"
To be consistent

While at first glance the method of section~\ref{sec:why-rational} seems
straightforward to implement and test, three challenges remain. The first is
comparing the effect of blame on the rational programmer across three different
mechanisms; second is the collection of a large number of representative
debugging scenarios; and third is finding a proper sampling strategy for the
huge space of possibilities. A coincidental challenge is the disparity of the
implementations of gradually typed languages. To eliminate this variable, the
authors use Racket, which is thus far the only language in which all three major
soundness mechanisms are available in a robust and comparable manner:
Typed Racket implements Natural, Shallow Racket~\citep{ttt21}
Transient, and plain Racket for Erasure.

>>>>

While at first glance the method of section~\ref{sec:why-rational} seems
straightforward to implement and test, three challenges remain. The first is
comparing the effect of blame on the rational programmer across three different
mechanisms; second is the collection of a large number of representative
debugging scenarios; and third is finding a proper sampling strategy for the
huge space of possibilities. A coincidental challenge is the disparity of the
implementations of gradually typed languages. To eliminate this variable, the
authors use Racket, which is thus far the only language in which all three major
semantic variants are available in a robust and comparable manner:
Typed Racket implements Natural, Shallow Racket~\citep{ttt21}
Transient, and plain Racket for Erasure.
